Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-05-05 ms/Accessory/Wenk-Accessory-SI.Rnw
Substantial reworking of Supp Matt for Accessories paper
- extract plant map images form power powerpoint
- fix table widths
- reorder materials, section headers etc

\usepackage{suppmat}
\usepackage{listings}
\usepackage[T1]{fontenc} % Better underscores
\usepackage{longtable}

@@

@@

print_table_metadata <- function(path) {

  data <-  read.csv(path, stringsAsFactors=FALSE, check.names=FALSE)
  file <- gsub("_", "\\_", basename(path), fixed = TRUE)
  print(xtable(data,
            hline.after=c(1),
            label=sprintf("tab:file_", file),
            caption=
              sprintf("Variables within the file `%s`. These definitions are defined within the file `%s` in the folder `data`.",
              gsub("\\_meta", "", file, fixed = TRUE), file)),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

@@

\tableofcontents

@@

\section{Additional results}

All computations implemented in \textsc{r} \citep{R-2015}.

@@

names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")

@@

\begin{table}[H]
\centering
\caption{Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.}
\label{tab:species}
\begin{tabular}{p{4cm}|p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
\hline
& \multicolumn{7}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
& \multicolumn{7}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
& \multicolumn{7}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS15)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

\clearpage
<<echo=FALSE, results='asis', warning=FALSE>>=
make_table_RA_shifts_with_age <- function() {
  xvar <- "repro_inv"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

TableS16 <- make_table_RA_shifts_with_age()

for(i in c(2,3,5,6,8,9)){
  TableS16[,i] <- format(TableS16[,i],digits=2,nsmall=2)
}
for(i in c(4,7,10)){
  TableS16[,i] <- format_p(TableS16[,i])
}

@

\begin{table}[H]
\centering
\caption{Shifts in accessory costs with shifts in age, plant size, or reproductive effort.}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
\hline
& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c|}{Accessory costs} \\
& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass (mg)}& \multicolumn{3}{c|}{vs. age} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS16)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

for(i in c(2,3,5,6)){
  TableS17[,i] <- format(TableS17[,i],digits=2,nsmall=2)
}
for(i in c(4,7)){
  TableS17[,i] <- format_p(TableS17[,i])
}
@

\begin{table}[H]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

acc_by_species$Slope <- format(acc_by_species$Slope,nsmall=2,digits=2)
acc_by_species$Slope_lowCI <- format(acc_by_species$Slope_lowCI,nsmall=2,digits=2)
acc_by_species$Slope_highCI <- format(acc_by_species$Slope_highCI,nsmall=2,digits=2)

@@

acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
acc_by_species$pval <- format_p(acc_by_species$pval)
acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
}
TableS19 <- make_table_Table2_using_propagule()
names(TableS19) <- c("costs","r$^2$","slope (95% CI)","p (slope test)")
@
\begin{table}[H]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
        # , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

for(i in c(2,3)){
  TableS18[,i] <- format(TableS18[,i],digits=2,nsmall=2)
}
for(i in c(4)){
  TableS18[,i] <- format_p(TableS18[,i])
}

@@

\begin{table}[H]
\centering
\caption{Count of buds initiated is well predicted by plant size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}p{1.25cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS18)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\section{Details on data from main text}

\section{Investment categories}

The file accessoryParts.yml contains, for each species, lists of reproductive tissues that fall into various tissue categories. These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself. Dividing reproductive investment into these categories requires, for each tissue type, knowing the count of parts that reach the key stages (pollinator-ready, onset of provisioning, mature seed) and the mass of parts at each stage.

\subsection{accessoryParts\_metadata}
Brief descriptions of each reproductive parts category in the file accessoryParts.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/accessoryParts_meta.csv")
@

\subsection{investment categories by species in accessoryParts.yml}
List for each species of reproductive tissue types included in each of the investment categories
<<echo=FALSE,results='asis'>>=
  ###("../../data/accessoryParts.yml")
@

\section{Details about input files}
List of data files.

\begin{enumerate}
\item accessory\_parts.yml
\item flowerCategories.csv and flowerCategories\_meta.csv
\item flowerParts.csv and flowerParts\_meta.csv
\item individuals.csv and individuals\_meta.csv
\item MultiplierTable.csv
\item reproduction.csv and reproduction\_meta.csv
\item seedMultiplier.csv
\end{enumerate}

The following files contain supplmentary data about the species and sites:

\begin{enumerate}
\item seedsize.csv and seedsize\_meta.csv
\item sites.csv and sites\_meta.csv
\item species.csv
\end{enumerate}

\subsection{floweringCategories}
This file contains a matrix of plant parts (rows) by species (columns). For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet. Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.

\subsection{floweringCategories\_metadata}
This files contains a matrix of plant parts (rows) by species (columns). For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.

\subsection{flowerParts}
Harvested and weighed flower parts, including collections from tagged individuals (once mature or at time of harvest) and from other individuals in the population (to estimate weight of specific plant parts). All plant parts included in a species' "plant map" have weights in this spreadsheet – or, in rare cases, entries are instead plants parts whose weight is used to calculate the weight of a plant part included in a "plant map". (A "plant map" shows the developmental trajectory of a flower or inflorescence from bud to seed for each species, indicating the flow or carbon as well as discarded parts.) If plant parts are collected from a tagged individual, this spreadsheet also indicates in which census periods this specific weight, rather than a species average, should be used for calculating that individual's reproductive investment. Plant parts all have counts and weights, while the subset of plant parts whose size varies, also have columns indicating height and diameter dimensions; the weight of the plant part at a specific size is then determined by either a regression or volume calculation. For a few plant parts, census data measure the length of stem or cone covered with flowers; for these situations, the segment length collected is also recorded, such that the number of flowers per unit length can be calculated.

\subsection{flowerParts\_metadata}
Brief descriptions of each data column in the file flowerParts, including units.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/flowerParts_meta.csv")
@

\subsection{Individuals}
This file contains a list of all plants harvested at the 7 Kuring'gai fieldsites. For each individual it includes basic information about each individual - tag number, age, site, whether the plant was alive at the time of harvest, and information on which calculations use this individual's data. The data itself is contained in other files.

\subsection{Individuals\_metadata}
Brief descriptions of each data column in the file Individuals, including units.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/Individuals_meta.csv")
@

\subsection{multiplierTable}
Lookup table indicating, for each species by flower part combination, if the investment per part is for a single (1) or multiple propagules, defined as either a mature fruit or a seed, depending on what is the dispersal unit for each species. Within a single column, i.e. within a single species developmental trajectory, numbers will change if the "count" used to access reproduction changes at a given developmental stage. For instance, with BOLE (Boronia ledifolia), counts are made by flowers up through the finished flower stage, but then fruit are the unit counted and each flower forms 4 fruit.

\subsection{reproduction}
The reproduction spreadsheet provides both verbal and numeric descriptions of reproduction at each census between April-June 2012 (or June 2013 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were first tagged, until April-June 2013 (or June 2014 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were harvested. There is a separate row of data for each individual, at each of the 18 censuses. In addition, at each census, there is a row indicating plant parts that are pre-existing on the plant versus new. Flower (or fruit) parts are considered pre-existing if the predecessor of that flower part, as described on that species "plant map" existed in a previous census period. Some plant maps may have multiple parallel diagrams describing how flower parts develop. In that case, a flower part must have a predecessor on that specific diagram to be considered "pre-existing".

Each of the many plant parts are listed as column headers. At each census, both new and further developed but pre-existing flower parts are recorded. Plant parts that are unchanged in developmental stage between successive censuses are not recorded. Neither are plant parts that disappear between successive censuses. Instead, pre-existing plant parts are recorded if they have progressed to a "more mature" flowering/fruiting stage, as defined by that species "plant map". As an example, if at one census there were 50 PHPH (Phyllota phylicoides) buds recorded and at the next stage, 30 PHPH flowers, 30 of the 50 buds progressed from being buds to being flowers, while the remaining 20 buds were either shed or are still buds. The numbers entered in the cell correspond to either counts, lengths, or dimensions, depending on the method indicated in the file titled "floweringCategories".

\subsection{reproduction\_metadata}
Brief descriptions of the first set of data columns in the file reproduction.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/reproduction_meta.csv")
@

\subsection{seedsize}
A collection of species level information, including seed size and embryo-endosperm weight. This file also includes data on the number of ovules per ovary, lifespan, age at maturity, and approximate age at which RA asymptotes.

\subsection{seedsize\_metadata}
Brief descriptions of the first set of data columns in the file seedsize, including units.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/seedsize_meta.csv")
@

\subsection{sites}
Tables of sites used in study. Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers, and UTM coordinates for each site.

\subsection{sites\_metadata}
Brief descriptions of the first set of data columns in the file sites

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/sites_meta.csv")
@

\subsection{species}
Table of species included in study. Includes 4-letter code names used in other spreadsheets, scientific names, family names, and common names.

\section{Overview of methods for estimating reproductive allocation}

\subsection{Overview of plant maps}

@@

The accompanying table for each species provides a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.

@@

The count of each reproductive tissue type was determined for each individual at each census time. For some reproductive parts a simple count is practical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure. These lengths were converted into counts through a species value of "flowers per length". For species that form cones, the cones can be notably different in size and each cone's dimensions was recorded throughout development. The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the file multiplierTable.

@@

\section{R scripts used to calculate reproductive investment}

\subsection{preprocess.R}

@@

\subsection{OrderedListOfParts.R}

@@

\subsection{FlowerParts.R}

@@

\subsection{GraphRepresentation.R}

@@

\subsection{Investment.R}

@@

\subsection{ReproductionTissues.R}

@@

\section{Details on calculations by species}

\subsection{Banksia ericifolia}

>>>>

\usepackage{suppmat}
\usepackage{listings}
\usepackage[T1]{fontenc} % Better underscores
\usepackage{longtable}
\usepackage{graphicx}

@@

% allow some pages to be landscape
\usepackage{lscape}

@@

print_table_metadata <- function(path, align = NULL) {

  data <-  read.csv(path, stringsAsFactors=FALSE, check.names=FALSE)
  file <- gsub("_", "\\_", basename(path), fixed = TRUE)

  label <- sprintf("tab:%s_meta", strsplit(basename(path), "_")[[1]][1])

  print(xtable(data,
            align=align,
            hline.after=c(1),
            label= label,
            caption=
              sprintf("Details on variables within the file \\texttt{%s}.",
              gsub("\\_meta", "", file, fixed = TRUE))),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

@@

\begingroup
\let\cleardoublepage\relax
\let\clearpage\relax
\tableofcontents
\endgroup

@@

\section{Additional results supporting main text}

@@

names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","success","discarded","success","discarded","pollen-attraction","provisioning")

@@

\begin{table}[H]
\centering
\caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.}
\label{tab:species}
\begin{tabular}{p{4cm}|p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
\hline
& \multicolumn{7}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
& \multicolumn{7}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
& \multicolumn{7}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\

% \begin{tabular}{p{3cm}|p{1cm}p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
% \hline
% &&&& \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
% &&&& \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
% &&&& \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\

<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS15)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}

{\color{red}
\begin{itemize}
  \item Started reworking table headers but have no idea what they're meant to be.
  \item Decrease decimal places?
  \item Swing page to landscape?
  \item Add units?
\end{itemize}
}

\end{table}

\clearpage
<<echo=FALSE, results='asis', warning=FALSE>>=
make_table_RA_shifts_with_age <- function(SummaryInd) {
  xvar <- "repro_inv"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

@@

TableS16 <- make_table_RA_shifts_with_age(SummaryInd)

for(i in c(2,3,5,6,8,9)){
  TableS16[,i] <- format_r2(TableS16[,i])
}
for(i in c(4,7,10)){
  TableS16[,i] <- format_p(TableS16[,i])
}
@

\begin{table}[H]
\centering
\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort.}
\label{tab:access_vs_age}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
\hline
& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass}& \multicolumn{3}{c}{vs. age} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS16)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

for(i in c(2,3,5,6)){
  TableS17[,i] <- format_r2(TableS17[,i])
}
for(i in c(4,7)){
  TableS17[,i] <- format_p(TableS17[,i])
}
@

\begin{table}[H]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'.}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

acc_by_species$Slope <- format_r2(acc_by_species$Slope)
acc_by_species$Slope_lowCI <- format_r2(acc_by_species$Slope_lowCI)
acc_by_species$Slope_highCI <- format_r2(acc_by_species$Slope_highCI)

@@

acc_by_species$r2 <- format_r2(acc_by_species$r2)
acc_by_species$pval <- format_p(acc_by_species$pval)
acc_by_species$Slope_test_p <- format_p(acc_by_species$Slope_test_p)
acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
}
TableS19 <- make_table_Table2_using_propagule()
names(TableS19) <- c("costs","r$^2$","slope (95$\\%$ CI)","p (slope test)")
@
\begin{table}[H]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size.}
\label{tab:repro_tissues_vs_prop_size}
\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
         , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

for(i in c(2,3)){
  TableS18[,i] <- format_r2(TableS18[,i])
}
for(i in c(4)){
  TableS18[,i] <- format_p(TableS18[,i])
}

@@

\begin{table}[H]
\centering
\caption{Count of buds initiated is well predicted by plant size.}
\label{tab:bud_count_vs_size}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}p{1.25cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS18)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\section{Additional details on methods and details about input files}

@@

Tables
The accompanying table for each species provides a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.

@@

The count of each reproductive tissue type was determined for each individual at each census time. For some reproductive parts a simple count is practical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure. These lengths were converted into counts through a species value of "flowers per length". For species that form cones, the cones can be notably different in size and each cone's dimensions was recorded throughout development. The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the file \texttt{multiplierTable.csv} (details below).

@@

\subsection{Details on calculations by species}

\subsubsection{Banksia ericifolia}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/BAER.png}
\caption{Map of parts for \emph{Banksia ericifolia}}
\label{fig:map Banksia ericifolia}
\end{figure}

\subsubsection{Boronia ledifolia}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/BOLE.png}
\caption{Map of parts for \emph{Boronia ledifolia}}
\label{fig:map Boronia ledifolia}
\end{figure}

\subsubsection{Conospermum ericifolium}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/COER.png}
\caption{Map of parts for \emph{Conospermum ericifolium}}
\label{fig:map Conospermum ericifolium}
\end{figure}

\subsubsection{Epacris microphylla}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/EPMI.png}
\caption{Map of parts for \emph{Epacris microphylla}}
\label{fig:map Epacris microphylla}
\end{figure}

\subsubsection{Grevillea buxifolia}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/GRBU.png}
\caption{Map of parts for \emph{Grevillea buxifolia}}
\label{fig:map Grevillea buxifolia}
\end{figure}

\subsubsection{Grevillea speciosa}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/GRSP.png}
\caption{Map of parts for \emph{Grevillea speciosa}}
\label{fig:map Grevillea speciosa}
\end{figure}

\subsubsection{Hakea teretifolia}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/HATE.png}
\caption{Map of parts for \emph{Hakea teretifolia}}
\label{fig:map Hakea teretifolia}
\end{figure}

\subsubsection{Hemigenia purpurea}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/HEPU.png}
\caption{Map of parts for \emph{Hemigenia purpurea}}
\label{fig:map Hemigenia purpurea}
\end{figure}

\subsubsection{Leucopogon esquamatus}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/LEES.png}
\caption{Map of parts for \emph{Leucopogon esquamatus}}
\label{fig:map Leucopogon esquamatus}
\end{figure}

\subsubsection{Persoonia lanceolata}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/PELA.png}
\caption{Map of parts for \emph{Persoonia lanceolata}}
\label{fig:map Persoonia lanceolata}
\end{figure}

\subsubsection{Petrophile pulchella}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/PEPU.png}
\caption{Map of parts for \emph{Petrophile pulchella}}
\label{fig:map Petrophile pulchella}
\end{figure}

\subsubsection{Phyllota phylicoides}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/PHPH.png}
\caption{Map of parts for \emph{Phyllota phylicoides}}
\label{fig:map Phyllota phylicoides}
\end{figure}

\subsubsection{Pimelea linifolia}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/PILI.png}
\caption{Map of parts for \emph{Pimelea linifolia}}
\label{fig:map Pimelea linifolia}
\end{figure}

\subsubsection{Pultenaea tuberculata}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{../plant_maps/crop/PUTU.png}
\caption{Map of parts for \emph{Pultenaea tuberculata}}
\label{fig:map Pultenaea tuberculata}
\end{figure}

\subsection{Structure of data files}

\begin{enumerate}
\item \texttt{accessory\_parts.yml}
\item \texttt{flowerCategories.csv}
\item \texttt{flowerParts.csv}
\item \texttt{individuals.csv}
\item \texttt{MultiplierTable.csv}
\item \texttt{reproduction.csv}
\item \texttt{seedMultiplier.csv}
\end{enumerate}
The following files contain supplementary data about the species and sites:
\begin{enumerate}
\item \texttt{seedsize.csv}
\item \texttt{sites.csv}
\item \texttt{species.csv}
\end{enumerate}

\subsubsection{Accessory Parts}

The file \texttt{accessoryParts.yml} contains, for each species, lists of reproductive tissues that fall into various tissue categories. These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself. Dividing reproductive investment into these categories requires, for each tissue type, knowing the count of parts that reach the key stages (pollinator-ready, onset of provisioning, mature seed) and the mass of parts at each stage. Table \ref{tab:accessoryParts_meta} provides descriptions of each reproductive part category in the file \texttt{accessoryParts.yml}.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/accessoryParts_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
@

\subsubsection{Flowering Categories}

The file \texttt{flowerCategories.csv} contains a matrix of plant parts (rows) by species (columns). For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet. Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.

The file \texttt{floweringCategories\_meta} contains a matrix of plant parts (rows) by species (columns). For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.

\subsubsection{Flower Parts}
The file \texttt{flowerParts.csv} contains records for harvested and weighed flower parts, including collections from tagged individuals (once mature or at time of harvest) and from other individuals in the population (to estimate weight of specific plant parts).  Table \ref{tab:flowerParts_meta} gives a brief descriptions of each column in the file.

All plant parts included in a species' "plant map" have weights in this spreadsheet – or, in rare cases, entries are instead plants parts whose weight is used to calculate the weight of a plant part included in a "plant map". (A "plant map" shows the developmental trajectory of a flower or inflorescence from bud to seed for each species, indicating the flow or carbon as well as discarded parts.) If plant parts are collected from a tagged individual, this spreadsheet also indicates in which census periods this specific weight, rather than a species average, should be used for calculating that individual's reproductive investment. Plant parts all have counts and weights, while the subset of plant parts whose size varies, also have columns indicating height and diameter dimensions; the weight of the plant part at a specific size is then determined by either a regression or volume calculation. For a few plant parts, census data measure the length of stem or cone covered with flowers; for these situations, the segment length collected is also recorded, such that the number of flowers per unit length can be calculated.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/flowerParts_meta.csv", align = 'p{0.1cm}p{4cm}p{2cm}p{10cm}')
@

\subsubsection{Individuals}
This file \texttt{individuals.csv} contains a list of all plants harvested at the 7 Kuring'gai field sites. For each individual it includes basic information about each individual - tag number, age, site, whether the plant was alive at the time of harvest, and information on which calculations use this individual's data. The data itself is contained in other files. Table \ref{Individuals_meta} gives a brief description of each data column in the file.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/Individuals_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
@

\subsubsection{Multiplier Table}
The file \texttt{MultiplierTable.csv} is a lookup table indicating, for each species by flower part combination, if the investment per part is for a single (1) or multiple propagules, defined as either a mature fruit or a seed, depending on what is the dispersal unit for each species. Within a single column, i.e. within a single species developmental trajectory, numbers will change if the "count" used to access reproduction changes at a given developmental stage. For instance, with BOLE (\emph{Boronia ledifolia}), counts are made by flowers up through the finished flower stage, but then fruit are the unit counted and each flower forms 4 fruit.

\subsubsection{Reproduction}

The file \texttt{reproduction.csv} provides both verbal and numeric descriptions of reproduction at each census between April-June 2012 (or June 2013 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were first tagged, until April-June 2013 (or June 2014 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were harvested. Table \ref{tab:reproduction_meta} gives a brief description of the columns in the file. There is a separate row of data for each individual, at each of the 18 censuses. In addition, at each census, there is a row indicating plant parts that are pre-existing on the plant versus new. Flower (or fruit) parts are considered pre-existing if the predecessor of that flower part, as described on that species "plant map" existed in a previous census period. Some plant maps may have multiple parallel diagrams describing how flower parts develop. In that case, a flower part must have a predecessor on that specific diagram to be considered "pre-existing".

Each of the many plant parts are listed as column headers. At each census, both new and further developed but pre-existing flower parts are recorded. Plant parts that are unchanged in developmental stage between successive censuses are not recorded. Neither are plant parts that disappear between successive censuses. Instead, pre-existing plant parts are recorded if they have progressed to a "more mature" flowering/fruiting stage, as defined by that species "plant map". As an example, if at one census there were 50 PHPH (\emph{Phyllota phylicoides}) buds recorded and at the next stage, 30 PHPH flowers, 30 of the 50 buds progressed from being buds to being flowers, while the remaining 20 buds were either shed or are still buds. The numbers entered in the cell correspond to either counts, lengths, or dimensions, depending on the method indicated in the file titled "floweringCategories".

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/reproduction_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
@

\subsubsection{Seed size}
The file \texttt{seedsize.csv} includes a collection of species level information, including seed size and embryo-endosperm weight. This file also includes data on the number of ovules per ovary, lifespan, age at maturity, and approximate age at which RA asymptotes. Table \ref{tab:seedsize_meta} gives a brief description of the data columns in the file.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/seedsize_meta.csv", align = 'p{0.1cm}p{4cm}p{10cm}p{2cm}')
@

\subsubsection{Sites}
The file \texttt{sites.csv} lists details of sites used in study. Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers, and UTM coordinates for each site. Table \ref{tab:sites_meta} gives a brief description of the data columns in the file.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/sites_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
@

\subsubsection{Species}
The file \texttt{species.csv} lists species included in study. Includes 4-letter code names used in other spreadsheets, scientific names, family names, and common names. Table \ref{tab:species} gives a brief description of the data columns in the file.

\subsection{Code calculating reproductive investment}

\subsubsection{preprocess.R}

@@

\subsubsection{OrderedListOfParts.R}

@@

\subsubsection{FlowerParts.R}

@@

\subsubsection{GraphRepresentation.R}

@@

\subsubsection{Investment.R}

@@

\subsubsection{ReproductionTissues.R}

@@
